Manuscript

### 2014-10-28 inst/simulation/manuscript.Rmd
...

plotLogPopulationSize <- function(size, meanSize, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)
  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    #geom_point(size=1) +
    #stat_smooth(method="lm", aes(colour=modelName), se=F) +
    geom_point(size=1, colour="darkgray") +
    stat_smooth(method="lm", se=F, colour="black") +
    #scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
    #scale_colour_manual("Model", values=c("darkgray","black")) +
    geom_abline(colour="black", linetype="longdash") + 
    #geom_point(data=meanSize, aes(True, Estimated, colour=modelName), size=2, shape=15) +
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black") +
    facet_wrap(~Scenario, scales="free") +
    coord_cartesian(xlim=xlim, ylim=ylim) +
    scale_x_log10() + scale_y_log10() +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=12))
  print(p)
  return(p)
}
```

@@

meanPopulationSizes2000  <- getMeanPopulationSizes(populationSizes2000)
logPopulationSizes2000 <- getLogPopulationSizes(populationSizes2000)
logMeanPopulationSize2000  <- getLogMeanPopulationSizes(populationSizes2000)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, full=F, file) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x) {
    y <- lm(Estimated~Observed, x)
    data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
  })
  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)

>>>>

plotLogPopulationSize <- function(size, meanSize, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    #geom_point(size=1) +
    #stat_smooth(method="lm", aes(colour=modelName), se=F) +
    geom_point(size=1, colour="darkgray") +
#stat_smooth(method="lm", se=F, colour="black") +
    #scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
    #scale_colour_manual("Model", values=c("darkgray","black")) +
    geom_abline(colour="black", linetype="longdash") + 
    #geom_point(data=meanSize, aes(True, Estimated, colour=modelName), size=2, shape=15) +
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black") +
    facet_wrap(~Scenario, scales="free") +
    coord_cartesian(xlim=xlim, ylim=ylim) +
    scale_x_log10() + scale_y_log10() +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=12))

  if (!any(abs(size$Estimated) == Inf)) p <- p + stat_smooth(method="lm", se=F, colour="black")

  print(p)
  return(p)
}
```

@@

meanPopulationSizes2000  <- getMeanPopulationSizes(populationSizes2000)
logPopulationSizes2000 <- getLogPopulationSizes(populationSizes2000)
logMeanPopulationSizes2000  <- getLogMeanPopulationSizes(populationSizes2000)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, full=F, file) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x) {
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA))
    y <- lm(Estimated~Observed, x)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2)))
  })
  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)
